EDIpack: A generic and interoperable Lanczos-based solver for quantum impurity problems

### 2025-05-24 05_examples.tex
Updates from Overleaf

  \item[{\tiny ${\it User} $>$ {\bf EDIpack}}] Optimize the bath parameters $\vec{x}$ against the updated
    Weiss field,  potentially using the conjugate gradient procedures 
supplied by \NAME. Then, restart at step 1.
\end{itemize}

>>>>

  \item[{\tiny {\it User} \textgreater\ {\bf EDIpack}}] Optimize the bath parameters $\vec{x}$ against the updated
    Weiss field,  potentially using the conjugate gradient procedures 
supplied by \NAME. Then, restart at step 1.
\end{itemize}
